Author's fourth reply to the referee report of \\ \textsc{ ``PERSISTENT HOMOLOGY FOR FUNCTIONALS'' }

### 2023-10-10 ref_reply4.tex
Before addressing 4th reply

\title{Author's third reply to the referee report of \\ \textsc{
		``PERSISTENT HOMOLOGY FOR FUNCTIONALS''
	}
}
\author{Bauer \and Medina-Mardones \and Schmahl}
\begin{document}
	\maketitle
	We want to thank the referee for once again reading our revised article very carefully and for taking the time to give us very helpful and detailed commentary throughout the review process going far beyond the usual scope of referee's reports. To express our gratitude, we have included a corresponding sentence in the acknowledgements section of the article.

>>>>

\title{Author's fourth reply to the referee report of \\ \textsc{
		``PERSISTENT HOMOLOGY FOR FUNCTIONALS''
	}
}
\author{Bauer \and Medina-Mardones \and Schmahl}
\begin{document}
	\maketitle
	We want to thank the referee for once again reading our revised article very carefully and for taking the time to give us very helpful and detailed commentary throughout the review process going far beyond the usual scope of referee's reports.
